Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-08-28 Manuscript/manuscript.Rmd
edits

Biological replicate Hi-C data were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1) for the GM12878 and K562 cell lines. The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox]. TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for all resolutions and cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line. [??? TBD, did you process the data yourself? Or, just downloaded coordinates. If the latter, why the whole mishmash of data processing description?]

@@

3. **Random Over-Sampling (ROS)**: All of the data points from the majority class of the training set were used. Sampling with replacement was used to obtain the same number of data points from the minority class. [??? I leave this unfinished because the definitions seem plain wrong]

>>>>

Biological replicate Hi-C data were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1) for the GM12878 and K562 cell lines. The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox]. TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for all resolutions and cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.

@@

3. **Random Over-Sampling (ROS)**: All of the data points from the majority class of the training set were used. Sampling with replacement from minority class was used to obtain the same number of data points as in the majority class.
